### 2012-06-15 inst/examples/Reed.Rmd
allee voi example

``` {r  echo=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
````

@@

``` {r }
f <- BevHolt
````

Note that the `pdg_control` pacakge already has a definition for the `BevHolt` function, (typing the function name prints the function)

``` {r }
BevHolt
````

That is, \( f(x,h) = \frac{A x}{1 + B x} \)

Of course we could pass in any custom function of stocksize `x`, harvest `h` and parameter vector `p` in place of `BevHolt`.  Note that we would need to write this function explicitly so that it can take vector values of `x` (i.e. uses `sapply`), an annoying feature of `R` for users comming from Matlab.

We must now define parameters for the function.  Note that the positive stationary root of the model is given by \( (A-1)/B \), which we'll store for future reference as `K`.

``` {r }
pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
````

@@

``` {r  profit}
profit <- profit_harvest(price=1, c0 = 0.01) 
````

@@

``` {r policyfn_plot}
qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement")
````

@@

``` {r valuefn_plot}
qplot(x_grid, opt$V, xlab="stock size", ylab="value")
````

@@

We can also look at the harvest dynamics:

``` {r  p2}
p1 + geom_line(aes(time, harvest, group = reps), alpha = 0.1, col="darkgreen")
````

This strategy is supposed to be a constant-escapement strategy. We can visualize the escapement:

``` {r  p3}
p1 + geom_line(aes(time, escapement, group = reps), alpha = 0.1, col="darkgrey")
````

### Visualizing the optimal policy
Note that when the boundary is sufficiently far away, i.e. for the first couple timesteps, the optimal policy is stationary.  The optimal policy is shown here over time, where the color indicates the harvest recommended for each possible stock value at that time (shown on the vertical axis).  Note that below a certain stock value, harvesting is not recommended and the dots turn red (Reed's constant escapement rule!)  However, at very low values, harvesting starts again (orange dots), because of the allee effect - these populations are doomed anyway, so may as well fish all that remains.

Note that interestingly, populations just below the allee threshold are given the chance to be rescued stochastically early on - that small chance that they recover is worth the expected loss.  The "no-harvest" zones stand out clearly in the red areas of this graph.

``` {r  policy, fig.width=9}
policy <- melt(opt$D)
policy_zoom <- subset(policy, x_grid[Var1] < max(dt$fishstock) )
p5 <- ggplot(policy_zoom) + 
  geom_point(aes(Var2, (x_grid[Var1]), col=h_grid[value])) + 
  labs(x = "time", y = "fishstock") +
  scale_colour_gradientn(colours = rainbow(4)) +
  geom_abline(intercept=opt$S, slope = 0) +
  geom_abline(intercept=xT, slope=0, lty=2)
p5
````

The harvest intensity is limited by the stock size.

``` {r  policy2, fig.width=10}
p6 <- ggplot(policy_zoom) + 
  geom_point(aes(Var2, (x_grid[Var1]), col=x_grid[Var1] - h_grid[value])) + 
  labs(x = "time", y = "fishstock") +
  scale_colour_gradientn(colours = rainbow(4)) +
  geom_abline(intercept=opt$S, slope = 0) +
  geom_abline(intercept=xT, slope=0, lty=2)
p6 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1, data=dt)
````

>>>>

``` {r  echo=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
#options(device = function(width = 5, height = 5) {
#    pdf(NULL, width = width, height = height)
#})
````

@@

``` {r }
f <- RickerAllee
K <- 4 
xT <- 2 # final value, also allee threshold
pars <- c(1.5, K, xT) 
````

@@

``` {r  profit}
profit <- profit_harvest(price=1, c0 = 0.01, c1=0) 
````

@@

``` {r policyfn_plot}
q1 <- qplot(x_grid, x_grid - x_grid[opt$D[,1]], xlab="stock size", ylab="escapement") + 
geom_point(aes(x,y), data=data.frame(x=opt$S, y=opt$S), col="red")
q1
````

@@

``` {r valuefn_plot}
q2 <- qplot(x_grid, opt$V, xlab="stock size", ylab="value") + 
geom_vline(xintercept=opt$S)
q2
````

@@

### 2012-06-15 inst/examples/value_of_information_allee.Rmd
allee voi example

# Calculating the value of information

 Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
 Compute the optimal solution under different forms of uncertainty.

@@

We consider a Beverton Holt state equation governing population dynamics, \\( f(x,h) = \frac{A x}{1 + B x} \\)

``` {r }
f <- BevHolt
````

With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.05`.

``` {r }
pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
````

Note that the positive stationary root of the model is given by \\( \frac{A-1}{B} \\), or carring capacity `K` = `r K`.  
We consider a profits from fishing to be a function of harvest `h` and stock size `x`,  \\( \Pi(x,h) = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\),

@@

``` {r runall}
det <- scenario(0, 0.0, 0.0)
g <- scenario(0.2, 0.0, 0.0)
m <- scenario(0.0, 0.2, 0.0)
i <- scenario(0.0, 0.0, 0.2)
gm <- scenario(0.2, 0.2, 0.0)
gi <- scenario(0.2, 0.0, 0.2)
gmi <- scenario(0.2, 0.2, 0.2)
````

``` {r not_all_zero}
det <- scenario(0.01, 0.0, 0.0)
````

@@

``` {r }
base <- simulatereps(det, 0, 0, 0)
reckless <- simulatereps(det, .2, .2, .2)
````

``` {r }
full <- simulatereps(gmi, .2, .2, .2)
cautious <- simulatereps(gmi, 0, 0, 0)
````

>>>>

# Calculating the value of information with highly nonlinear value function

 Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
 Compute the optimal solution under different forms of uncertainty, but under strong allee dynamics

@@

We consider the state dynamics

``` {r }
f <- RickerAllee
K <- 4 
xT <- 2 # final value, also allee threshold
pars <- c(1.5, K, xT) 
f
````

We consider a profits from fishing to be a function of harvest `h` and stock size `x`,  \\( \Pi(x,h) = h - \left( c_0  + c_1 \frac{h}{x} \right) \frac{h}{x} \\), conditioned on \\( h > x \\) and \\(x > 0 \\),

@@

``` {r runall}
det <- scenario(0, 0.0, 0.0)
g <- scenario(0.1, 0.0, 0.0)
m <- scenario(0.0, 0.1, 0.0)
i <- scenario(0.0, 0.0, 0.1)
gm <- scenario(0.1, 0.1, 0.0)
gi <- scenario(0.1, 0.0, 0.1)
gmi <- scenario(0.1, 0.1, 0.1)
````

``` {r not_all_zero}
det <- scenario(0.001, 0.0, 0.0)
````

@@

``` {r }
base <- simulatereps(det, 0, 0, 0)
reckless <- simulatereps(det, .1, .1, .1)
````

``` {r }
full <- simulatereps(gmi, .1, .1, .1)
cautious <- simulatereps(gmi, 0, 0, 0)
````
